MyPDDL: Tools for efficiently creating PDDL domains and problems

### 2020-08-14 paper.tex
final version

\usepackage{hyperref}
\usepackage{graphicx}
\graphicspath{{img/}}
\usepackage{tabularx}
\newcommand{\tableheadline}[1]{\multicolumn{1}{c}{#1}}
\usepackage{dirtree}
\usepackage{rotating}
\usepackage{caption}
\usepackage{booktabs}

% More space between rows:		
\renewcommand{\arraystretch}{1.1}		
% Slightly more space between columns:		
\setlength{\tabcolsep}{8pt}
\usepackage{minted}
\definecolor{dhscodebg}{rgb}{0.95,0.95,0.95} % listing background
%\DeclareUnicodeCharacter{2212}{-}

@@

Being a key aspect of artificial intelligence, \emph{planning} is
concerned with devising a sequence of actions to achieve a desired
goal \cite{helmert2008understanding}. It can be both a tool to create
automated systems and a means to support and understand human
behavior~\cite{konar1999artificial}. However, the effectiveness of
planning largely depends on the quality of the problem formalization
\cite{shah2013knowledge}. To ensure a standardized modeling format,
\pddl (\emph{Planning Domain Definition Language})
\cite{mcdermott1998pddl} was developed and has become the de facto
standard for the description of planning tasks
\cite{ilghami2005extension}. The discipline that deals with the
integration of world information into a computer system via a human
expert is called knowledge engineering \cite{feigenbaum1983fifth}.
While automated planning could save vast amounts of time if everything
works as intended, creating the planning task specifications is a
complex task that can be error-prone and cumbersome.

In this chapter, we describe \mypddl
(Figure~\ref{fig:mypddl-overview}), a knowledge engineering toolkit
that supports the knowledge engineer in the entire design cycle of
specifying planning tasks. In the initial stages, it allows for the
creation of structured \pddl projects that should encourage a
disciplined design process. With the help of snippets, that is, code
templates, often used syntactic constructs can be inserted into \pddl
files. A syntax highlighting feature that speeds up the
error-detection can come in handy in intermediate
stages. Understanding the textual representation of complex type
hierarchies in domain files can be confusing, so an additional tool
enables their visualization. \pddl's limited modeling capabilities
were bypassed by developing an interface that converts \pddl code into
code of the functional programming language Clojure
\cite{hickey2008clojure} and vice versa.  Within this project, the
interface was employed for a feature that calculates distances between
objects specified in a problem model, but the interface provides
numerous other possibilities and could also be used to further
automate the modeling process. A basic planner integration allows for
quickly running a desired planner. All of the features were integrated
into the customizable and extensible Sublime
Text\footnote{\url{http://www.sublimetext.com/}} editor. Since the
main aim in the development of the toolkit was for it to be easy to
use and maintain, it is evaluated with regard to these criteria. The
usability was assessed by means of a user test with eight subjects
that had no prior experience with AI planning. The results indicate
that both error-detection and the understanding of a given domain can
be facilitated by \mypddl.

\begin{figure}[H]
  \centering
  \tikzstyle{every node}=[draw=black,anchor=west,
  align=left,
  scale=0.7]
  \begin{tikzpicture}[%
  grow via three points={one child at (0.5,-0.7) and
    two children at (0.5,-0.7) and (0.5,-1.4)},
  edge from parent path={(\tikzparentnode.south) |- (\tikzchildnode.west)}]
  \node {~~~\textbf{myPDDL}~~~}
  child { node {\textbf{-new}\\Create new \pddl project}}
  child { node {\textbf{-snippet}\\Code templates}}
  child { node {\textbf{-syntax}\\Context-aware syntax highlighting}}
  child { node {\textbf{-clojure}\\Preprocessor for \pddl files via Clojure}}
  child { node {\textbf{-distance}\\Distance calculation in spatial domains}}
  child { node {\textbf{-diagram}\\Visualization of type hierarchy}}
  child { node {\textbf{-plan}\\Planner integration}};
  \end{tikzpicture}
    \caption{\mypddl is a highly customizable and extensible modular
    system, designed for supporting knowledge engineers in the process
    of writing, analyzing and expanding PDDL files and thereby
    promoting the collaboration between knowledge engineers and the
    use of PDDL in real-world applications. It consists of the parts
    shown in the figure.}
  \label{fig:mypddl-overview}  
\end{figure}

@@

\pddlstudio \cite{plch2012inspect} is an IDE (\emph{integrated
  development environment}) for creating and managing \textsc{pddl}
projects, that is, a collection of \textsc{pddl} files. Its main
features are syntax highlighting, error detection, context sensitive
code completion, code folding, project management, and planner
integration. Many of these features are based on a parser, which
continuously analyzes the code and divides it into syntactic
elements. These elements and the way in which they relate to each
other can then be identified. The syntax highlighter is a tool that
colors constructs according to their syntactical meaning within the
code. In the case of \pddlstudio, it colors names, variables, errors,
keywords, predicates, types, and brackets each in a different
customizable color.  \pddlstudio's error detection can recognize both
syntactic (missing keywords, parentheses, etc.) and semantic (wrong
type of predicate parameters, misspelled predicates, etc.)
errors. This means that \pddlstudio can detect errors based on a
mismatch between domain and problem file in real time. The code
completion feature offers recommendations for standard standard
\textsc{pddl} constructs as well as for previously used terms. Code
folding allows the knowledge engineer to hide currently not needed
code blocks. In this case only the first line of the block is
displayed. Lastly, a command-line interface allows the integration of
planners in order to run and compare different planning software.

@@

The online tool \epd allows for editing \pddl files in a web
browser. Its feature comprise syntax highlighting, code folding,
\pddl-specific auto-completion, and multi-tab support. The editor is
part of the Planning-Domains\footnote{\url{http://planning.domains/}}
initiative which aims at providing three pillars to the planning
community: (1) an API to access existing \pddl domains and problems;
(2) a planner-in-the-cloud service which be be accessed via a RESTful
API; and (3) an online \pddl editor. The online editor is also
connected to the planner in the cloud.

@@

\pddlstudio, \itsimple, and \epd for the most part do not build on
existing editors and therefore cannot fall back on refined
implementations of features, such as selection of tab size, defining
custom key shortcuts, customizing the general look and feel, and
bracket matching. In contrast, \vscode is integrated into the
mature editor Visual Studio Code and can be used in combination with
other plugins. To have both basic editor features and a high
customizability, it was decided to use an existing, extensible text
editor to integrate \mypddl into.

@@

Another feature that can be useful for fast development is the ability
to insert larger code skeletons or snippets. \pddlstudio does not
support the insertion of code snippets. \itsimple features some code
templates for predicates, derived predicates, functions, actions,
constraints, types, comments, requirements, objects, and
metrics. However, the templates are neither customizable nor
extensible. \pddlmode for Emacs provides three larger skeletons: one
for domains, one for problems, and one for actions. Further skeletons
could be added. Both \epd and \vscode provide many code
snippets. \mypddl aims to combine the best of these latter tools and
support customizable and extensible snippets for domains, problems,
types, predicates, functions, actions, and durative actions.

@@

\pddlstudio falls short of customization options since they are
limited to the choice of font style and color of highlighted \pddl
expressions. Furthermore, \pddlstudio is written as standalone
program, meaning that there are no \pddl-independent extensions. The
same holds true for \itsimple. Since both Emacs and VS Code are
established editors, \pddlmode and \vscode are highly customizable and
extensible. This is the other major reason why it was decided that
\mypddl should be integrated into a existing, extensible, and
customizable text editor. These requirements are met by Sublime Text,
a text editor that offers a wide variety of features and plugins.

@@

For example, typing \texttt{action} and pressing the tabulator key
inserts a skeleton to specify an action. \pddl constructs with a
specified arity can be generated by adding the arity number to the
trigger (\texttt{p2} would insert the binary predicate template
\texttt{(pred-name~?x~-~object~?y~-~object)}.

@@

The two most central modules of \mypddl are \mypddlsyntax and
\mypddldiagram, since they support collaboration, efficiency, and
debugging independently of the user’s experience with \pddl. To
evaluate their usability, they were evaluated in a user study. To this
end, we compared the user performance regarding several tasks, both
with and without using the respective module.

@@

We defined four tasks: two debugging tasks for testing the syntax
highlighting feature and two type hierarchy tasks for testing the type
diagram generator. A within subjects design was considered most suited
due to the small number of participants. Therefore, it was necessary to
construct two tasks matched in difficulty for each of these two
types to compare the effects of having the tools available. Each
participant started either with a debugging or type hierarchy task and
was given the \mypddl tools either in the first two tasks or the
second two tasks, so that each participant completed each task type
once with and once without \mypddl. This results in $2$ (first task is
debugging or hierarchy) $\times$ $2$ (task variations for debugging
and hierarchy) $\times$ $2$ (starting with or without \mypddl) $= 8$
individual task orders, one per participant.

@@

\subsubsection{Analysis}

\begin{itemize}
\item Debugging Tasks: \nopagebreak To compare differences in the
  debugging tasks, a paired sample $t$-test was used; normality was
  tested with a Shapiro-Wilk test. To compare the arithmetic means
  ($M$s) of detected errors, the test was performed two-tailed, since
  syntax highlighting might both help or hinder the
  participants. Arithmetic standard deviations ($SD$s) were calculated
  for each condition.

@@

  The participants detected more errors using the syntax highlighting
  feature, ($M = 7.6$, $SD = 2.07$) than without it ($M = 10.3$,
  $SD = 3.45$); $t(7) = 2.68$, $p = 0.03$.  That is, approximately
  36\,\% more errors were found with syntax highlighting. The
  arithmetic means are displayed in Figure
  \ref{fig:found-errors-combined}, where each cross~($\times$)
  represents the data value of one participant.
\begin{figure}[h]
  \centering
  \hspace{1.7cm}
  \includegraphics[width=0.7\textwidth]{found_errors}
  \caption[Diagram of detected errors]{Comparison of detected errors
    with and without the syntax highlighting feature. Each cross
    ($\times$) shows the data value of one participant. The bars
    display the arithmetic mean.}
\label{fig:found-errors-combined}
\end{figure}

@@

  \begin{table}[]
    \centering
    \begin{tabular}{rrrrrrrr}
    \toprule
         & \multicolumn{4}{c}{Type Diagram Generator} & & &                                                                   \\
         & \multicolumn{2}{c}{with}                   & \multicolumn{2}{c}{without} &      &       &                     \\
\cmidrule(r){2-3}\cmidrule(r){4-5}
Question & $GM$                                       & $GSD$                       & $GM$ & $GSD$ & $df$ & $t$   & $p$  \\
\midrule
      Q1 & 21.8                                       & 1.52                        & 40.0 & 2.26  & 7    & -1.86 & 0.11 \\
      Q2 & 23.8                                       & 1.49                        & 50.8 & 2.16  & 7    & -1.91 & 0.10 \\
      Q3 & 48.0                                       & 3.49                        & 83.2 & 2.20  & 5    & -0.86 & 0.43 \\
      Q4 & 84.3                                       & 2.22                        & 54.1 & 1.93  & 1    & 4.48  & 0.14 \\
      Q5 & 41.2                                       & 2.24                        & 78.0 & 1.48  & 7    & -2.75 & 0.03 \\
\bottomrule
    \end{tabular}

    \caption{Overview of geometric means ($GM$s), geometric standard deviations ($GSD$s), degrees of freedom ($df$), $t$-values, and $p$-values. The calculation for Q4 is based on only two paired data values ($df = 1$). This table only considers paired data values, this means only if a participant answered the question correctly in both domains, the data value is considered (since \emph{paired} $t$-tests are calculated). In contrast, Figure \ref{fig:task-completions-agg} displays the geometric means for all correct answers.}

    \label{tab:p-values}
  \end{table}

\begin{figure}[h]
\captionsetup{singlelinecheck=off}
  \centering
  \hspace{1.7cm}
  \includegraphics[width=0.85\textwidth]{task_time}
  \caption[Diagram of the task completion time]{Task completion time
    for the type hierarchy tasks. The bars display the geometric mean
    averaged over all participants; each cross~($\times$) represents
    the data value of one participant. The percent values at the
    bottom of the bars show the percentage of users that completed the
    task successfully. The questions can be found in the
    Appendix~\ref{splisus} and
    \ref{store}.}\label{fig:task-completions-agg}
\end{figure}

@@

  While, in general, the syntax highlighting feature was considered
  very useful, two participants remarked that the used colors confused
  them and that they found them more distracting than helpful. One of
  them mentioned that the contrast of the colors was so low that they
  were hard for her to distinguish. She found the same number of
  errors with and without syntax highlighting. The other of the two
  was the only participant who found less errors with syntax
  highlighting than without it. With \mypddlsyntax, two participants
  found all errors in the domain, while none achieved this without
  syntax highlighting.

>>>>

\usepackage{hyperref}
\usepackage{graphicx}
\graphicspath{{img/}}
\usepackage{tabularx}
\newcommand{\tableheadline}[1]{\multicolumn{1}{c}{#1}}
\usepackage{dirtree}
\usepackage{rotating}
\usepackage{booktabs}

% More space between rows:		
\renewcommand{\arraystretch}{1.1}		
% Slightly more space between columns:		
\setlength{\tabcolsep}{8pt}
\usepackage{minted}
\definecolor{dhscodebg}{rgb}{0.95,0.95,0.95} % listing background
\DeclareUnicodeCharacter{2212}{-}

@@

Being a key aspect of artificial intelligence (AI), \emph{planning} is
concerned with devising a sequence of actions to achieve a desired
goal~\cite{helmert2008understanding}. AI planning has made remarkable
progress in solving planning problems in large state spaces that would
be impossible for humans to handle. The International Planning
Competition\footnote{\url{http://www.icaps-conference.org/index.php/Main/Competitions/}}
has led to a number of open source planners that are ready to be used
by practitioners and researchers outside the AI planning field.

However, the effectiveness of planning largely depends on the quality
of the problem formalization~\cite{shah2013knowledge}. \pddl
(\emph{Planning Domain Definition Language})~\cite{mcdermott1998pddl}
is the de facto standard for the description of planning
tasks~\cite{ilghami2005extension}. It divides the description of a
planning task into a domain model and problem descriptions: the
description of a household with its objects and locations would be a
domain, with possible tasks such as making breakfast, cleaning the
windows, or changing a light bulb. Someone with a non-planning
background, for example, from robotics, has to get used to the \pddl
syntax and its possibilities to describe the world. She also has to
keep track of the facts in the domain model and the different planning
tasks. While automated planning can save vast amounts of time to find
a valid solution, creating the planning task specifications is a
complex, error-prone, and cumbersome task. An ill-defined problem is
often the reason for finding suboptimal plans or no plan at all.  The
household domain in this example comes with another challenge. For
many tasks the distances between objects or other numerical input may
be necessary. \pddl is by its very nature as a planning language
designed for symbolic specifications. To use numerical data
efficiently, it must often be preprocessed.

In this chapter, we describe
\mypddl~(Figure~\ref{fig:mypddl-overview}), a knowledge engineering
toolkit that supports knowledge engineers in the entire design cycle
of specifying planning tasks without having to become an expert in AI
planning. In the initial stages, it allows for the creation of
structured \pddl projects that should encourage a disciplined design
process. With the help of snippets, that is, code templates, often
used syntactic constructs can be inserted into \pddl files. A syntax
highlighting feature that speeds up the error-detection supports
intermediate stages. Understanding the textual representation of
complex type hierarchies in domain files can be confusing, so an
additional tool enables their visualization. \pddl's limited modeling
capabilities were bypassed by developing an interface that converts
\pddl code into code of the functional programming language Clojure
\cite{hickey2008clojure} and vice versa.  Within this project, the
interface was employed for a feature that calculates distances between
objects specified in a problem model, but the interface provides
numerous other possibilities and could also be used to further
automate the modeling process. A basic planner integration allows for
quickly running a desired planner. All of the features were integrated
into the customizable and extensible Sublime
Text\footnote{\url{http://www.sublimetext.com/}} editor.

Since the main aim in the development of the toolkit was for it to be
easy to use and maintain, it is evaluated with regard to these
criteria. Another aim was to make planning more accessible in
real-life tasks and to enable inexperienced users to get started with
planning problems. Therefore, \mypddl's usability was assessed by
means of a user test with eight subjects that had no prior experience
with AI planning. The results show that \mypddl facilitates both
error-detection and the understanding of a given domain.

\begin{figure}[H]
  \centering
  \tikzstyle{every node}=[draw=black,anchor=west,
  align=left,
  scale=0.7]
  \begin{tikzpicture}[%
  grow via three points={one child at (0.5,-0.7) and
    two children at (0.5,-0.7) and (0.5,-1.4)},
  edge from parent path={(\tikzparentnode.south) |- (\tikzchildnode.west)}]
  \node {~~~\textbf{myPDDL}~~~}
  child { node {\textbf{-new}\\Create new \pddl project}}
  child { node {\textbf{-snippet}\\Code templates}}
  child { node {\textbf{-syntax}\\Context-aware syntax highlighting}}
  child { node {\textbf{-clojure}\\Preprocessor for \pddl files via Clojure}}
  child { node {\textbf{-distance}\\Distance calculation in spatial domains}}
  child { node {\textbf{-diagram}\\Visualization of type hierarchy}}
  child { node {\textbf{-plan}\\Planner integration}};
  \end{tikzpicture}
    \caption{\mypddl is a highly customizable and extensible modular
    system, designed for supporting knowledge engineers in the process
    of writing, analyzing and expanding \pddl files and thereby
    promoting the collaboration between knowledge engineers and the
    use of \pddl in real-world applications. It consists of the parts
    shown in the figure.}
  \label{fig:mypddl-overview}  
\end{figure}

@@

\pddlstudio \cite{plch2012inspect} is an IDE (\emph{integrated
  development environment}) for creating and managing \textsc{pddl}
projects, that is, a collection of \textsc{pddl} files. Its main
features are syntax highlighting, error detection, context sensitive
code completion, code folding, project management, and planner
integration. Many of these features are based on a parser, which
continuously analyzes the code and divides it into syntactic
elements. These elements and the way in which they relate to each
other can then be identified. The syntax highlighter is a tool that
colors constructs according to their syntactical meaning within the
code. In the case of \pddlstudio, it colors names, variables, errors,
keywords, predicates, types, and brackets each in a different
customizable color.  \pddlstudio's error detection can recognize both
syntactic (missing keywords, parentheses, etc.) and semantic (wrong
type of predicate parameters, misspelled predicates, etc.)
errors. This means that \pddlstudio can detect errors based on a
mismatch between domain and problem file in real time. The code
completion feature offers recommendations for standard \textsc{pddl}
constructs as well as for previously used terms. Code folding allows
the knowledge engineer to hide currently not needed code blocks. In
this case only the first line of the block is displayed. Lastly, a
command-line interface allows the integration of planners in order to
run and compare different planning software.

@@

The online tool \epd allows for editing \pddl files in a web
browser. Its features comprise syntax highlighting, code folding,
\pddl-specific auto-completion, and multi-tab support. The editor is
part of the Planning-Domains\footnote{\url{http://planning.domains/}}
initiative which aims at providing three pillars to the planning
community: (1) an API to access existing \pddl domains and problems;
(2) a planner-in-the-cloud service which be be accessed via a RESTful
API; and (3) an online \pddl editor. The online editor is also
connected to the planner in the cloud.

@@

\pddlstudio, \itsimple, and \epd for the most part do not build on
existing editors and therefore cannot fall back on refined
implementations of features, such as selection of tab size, defining
custom key shortcuts, customizing the general look and feel, and
bracket matching. In contrast, \vscode and \pddlmode for Emacs are
integrated into mature code editors and can be used in combination
with other plugins. To have both basic editor features and a high
customizability, it was decided to use an existing, extensible text
editor to integrate \mypddl into.

@@

Another useful feature for fast development is the ability to insert
larger code skeletons or snippets. \pddlstudio does not support the
insertion of code snippets. \itsimple features some code templates for
predicates, derived predicates, functions, actions, constraints,
types, comments, requirements, objects, and metrics. However, the
templates are neither customizable nor extensible. \pddlmode for Emacs
provides three larger skeletons: one for domains, one for problems,
and one for actions. Further skeletons could be added. Both \epd and
\vscode provide many code snippets. \mypddl aims to combine the best
of these latter tools and support customizable and extensible snippets
for domains, problems, types, predicates, functions, actions, and
durative actions.

@@

\pddlstudio falls short of customization options since they are
limited to the choice of font style and color of highlighted \pddl
expressions. Furthermore, \pddlstudio is written as standalone
program, meaning that there are no \pddl-independent extensions. The
same holds true for \itsimple. Since both Emacs and VS Code are
established editors, \pddlmode and \vscode are highly customizable and
extensible. This is the other major reason why it was decided that
\mypddl should be integrated into an existing, extensible, and
customizable text editor. These requirements are met by Sublime Text,
a text editor that offers a wide variety of features and plugins.

@@

For example, typing \texttt{action} and pressing the tabulator key
inserts a skeleton to specify an action. \pddl constructs with a
specified arity can be generated by adding the arity number to the
trigger (\texttt{p2} would insert the binary predicate template
\texttt{(pred-name~?x~-~object~?y~-~object)}).

@@

The two most central modules of \mypddl are \mypddlsyntax and
\mypddldiagram, since they support collaboration, efficiency, and
debugging independently of the user's experience with \pddl. To
evaluate their usability, they were evaluated in a user study. To this
end, we compared the user performance regarding several tasks, both
with and without using the respective module.

@@

We defined four tasks (Appendix~\ref{sub:tasks}): two debugging tasks
for testing the syntax highlighting feature and two type hierarchy
tasks for testing the type diagram generator. A within subjects design
was considered most suited due to the small number of
participants. Therefore, it was necessary to construct two tasks
matched in difficulty for each of these two types to compare the
effects of having the tools available. Each participant started either
with a debugging or type hierarchy task and was given the \mypddl
tools either in the first two tasks or the second two tasks, so that
each participant completed each task type once with and once without
\mypddl. This results in $2$ (first task is debugging or hierarchy)
$\times$ $2$ (task variations for debugging and hierarchy) $\times$
$2$ (starting with or without \mypddl) $= 8$ individual task orders,
one per participant.

@@

\newpage
\subsubsection{Analysis}
\begin{itemize}
\item Debugging Tasks: To compare differences in the
  debugging tasks, a paired sample $t$-test was used; normality was
  tested with a Shapiro-Wilk test. To compare the arithmetic means
  ($M$s) of detected errors, the test was performed two-tailed, since
  syntax highlighting might both help or hinder the
  participants. Arithmetic standard deviations ($SD$s) were calculated
  for each condition.

@@

  The participants detected more errors using the syntax highlighting
  feature ($M = 10.3$, $SD = 3.45$) than without it ($M = 7.6$,
  $SD = 2.07$); $t(7) = 2.68$, $p = 0.03$.  That is, approximately
  36\,\% more errors were found with syntax highlighting. The
  arithmetic means are displayed in Figure
  \ref{fig:found-errors-combined}, where each cross~($\times$)
  represents the data value of one participant.
\begin{figure}[h]
  \centering
  \hspace{1.7cm}
  \includegraphics[width=0.7\textwidth]{found_errors}
  \caption[Diagram of detected errors]{Comparison of detected errors
    with and without the syntax highlighting feature. Each cross
    ($\times$) shows the data value of one participant. The bars
    display the arithmetic mean.}
\label{fig:found-errors-combined}
\end{figure}

@@

  \begin{table}[]
    \centering
    \begin{tabular}{rrrrrrrr}
    \toprule
         & \multicolumn{4}{c}{Type Diagram Generator} & & &                                                                   \\
         & \multicolumn{2}{c}{with}                   & \multicolumn{2}{c}{without} &      &       &                     \\
\cmidrule(r){2-3}\cmidrule(r){4-5}
Question & $GM$                                       & $GSD$                       & $GM$ & $GSD$ & $df$ & $t$   & $p$  \\
\midrule
      Q1 & 21.8                                       & 1.52                        & 40.0 & 2.26  & 7    & -1.86 & 0.11 \\
      Q2 & 23.8                                       & 1.49                        & 50.8 & 2.16  & 7    & -1.91 & 0.10 \\
      Q3 & 48.0                                       & 3.49                        & 83.2 & 2.20  & 5    & -0.86 & 0.43 \\
      Q4 & 84.3                                       & 2.22                        & 54.1 & 1.93  & 1    & 4.48  & 0.14 \\
      Q5 & 41.2                                       & 2.24                        & 78.0 & 1.48  & 7    & -2.75 & 0.03 \\
\bottomrule
    \end{tabular}
    \caption{Overview of geometric means ($GM$s), geometric standard deviations ($GSD$s), degrees of freedom ($df$), $t$-values, and $p$-values. The calculation for Q4 is based on only two paired data values ($df = 1$). This table only considers paired data values, this means only if a participant answered the question correctly in both domains, the data value is considered (since \emph{paired} $t$-tests are calculated). In contrast, Figure \ref{fig:task-completions-agg} displays the geometric means for all correct answers.}
    \label{tab:p-values}
  \end{table}

\begin{figure}[h]
  \centering
  \hspace{1.7cm}
  \includegraphics[width=0.85\textwidth]{task_time}
  \caption[Diagram of the task completion time]{Task completion time
    for the type hierarchy tasks. The bars display the geometric mean
    averaged over all participants; each cross~($\times$) represents
    the data value of one participant. The percent values at the
    bottom of the bars show the percentage of users that completed the
    task successfully. The questions can be found in the
    Appendix~\ref{splisus} and
    \ref{store}.}\label{fig:task-completions-agg}
\end{figure}

@@

  While, in general, the syntax highlighting feature was considered
  very useful, two participants remarked that the used colors confused
  them and that they found them more distracting than helpful. One of
  them mentioned that the contrast of the colors was so low that they
  were hard for her to distinguish. She found the same number of
  errors with and without syntax highlighting. The other of the two
  was the only participant who found less errors with syntax
  highlighting than without it. With \mypddlsyntax, two participants
  found all errors in the domain, while none achieved this without
  syntax highlighting. While every participant had to use the same
  color scheme in the experiment, colors are customizable in
  \sublimetext.
